A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-11 JTB_supp/JTB_supp.Rmd
separate FigS9 calc and plot

# Figure S9. Hysteresis under different nutrient and feeding regimes.
```{r FigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

# Collect results
res1 <- cbind(input, output1)
res2 <- cbind(input, output2)
res3 <- cbind(input, output3)
res4 <- cbind(input, output4)

# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1))

>>>>

# Figure S9. Hysteresis under different nutrient and feeding regimes.
```{r runFigS9, cache=T, include=F}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

# Collect results
res1 <- cbind(input, output1)
res2 <- cbind(input, output2)
res3 <- cbind(input, output3)
res4 <- cbind(input, output4)
```

```{r plotFigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F}
# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1))
